ERSPAN Support for Linux

### 2018-10-16 paper.tex
fix Greg's comments

\begin{figure}
{\scriptsize
\begin{verbatim}
                             Linux                    Linux
+----------+         +-------------------+      +---------------+
| Physical |         |     VM1  VM2 ...  |      |     linux     |
| Machines |         |      |    |       |      |    netdevs    |
+----------+         |  +--------------+ |      |      |        |
    | links          |  | Open vSwitch | |      | ERSPAN        |
    |                |  +--------------+ |      | netdev        |
+------------+       +-------||----------+      +-||------------+ 
|Cisco switch|               ||                   ||
+------------+               || ERSPAN            || ERSPAN
   || ERSPAN tunnel          || tunnel            || tunnel
   ||                        ||                   ||
    /~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\     +-------+ 
    {       Layer 3 IPv4, Ipv6 network             } === |Traffic|
    \~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~/     |Sniffer|
                                                         +-------+
\end{verbatim}   
}
\vspace{-0.5em}
\caption{Overview of the ERSPAN tunnel use cases. ERSPAN tunnel can be
created between }
\label{overview}
\vspace{-1.0em}
\end{figure}

ERSPAN is popular in the followin use cases~\cite{erspan_ietf}:
\begin{itemize}
\item Debugging network issues by tracking the control and data frames. 
\item Monitoring Voice-over-IP, VoIP, packets for delay and jitter analysis
\item Monitoring network transactions for latency analysis
\item Monitoring network traffic for anomaly detection
\end{itemize}
Figure~\ref{overview} shows an example setup of ERSPAN tunnels.
A network administrator first sets up multiple source network devices
and filters the interested portion of the traffic he/she wants
to inspect.  One case on the left-most is to create the ERSPAN tunnel
between the Cisco switch and a traffic sniffer.  Depending on the
features in the Cisco switch, different filters can be applied to the
traffic.  In the middle of the figure, for multiple virtual machines running
inside a Linux box, the virtual switch forwarding the packet between
virtual and physical network can also create ERSPAN tunnels between
the software switch and remote traffic sniffer.
Here, Open vSwitch~\cite{ovs} is an example capabale of creating filters
and forward packets to ERSPAN tunnels. More detailed configurations of
Open vSwitch is described in later section.

@@

Mirrored traffic arrives at the sniffer machine needs to be able to
extract and restore the original monitored frame.  To differentiated
the three use cases, the administrator can create three ERSPAN session
ID, a configuration parameter for grouping the mirrored traffic.
For Linux user, an ERSPAN tunnel can also be used at the sniffer size.
Any packet arriving at the ERSPAN tunnel netdev's receive queue will
be decapsulated. Tools such as Wireshark~\cite{wireshark_erspan,wireshark_erspan2}
can be used to inspect the mirrored packet.

\section{ERSPAN Protocol Implementation}
\begin{figure}
{\scriptsize
\begin{verbatim}
<------------ outer -------------> <---- inner ---- ...
+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
| Ether |  IP  |  GRE  |  ERSPAN  | Ether |  IP  | ...   
+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
\end{verbatim}
}
\vspace{-1.0em}
\caption{An example of mirrored packet with outer header containing
the GRE and ERSPAN header, followed by the innter Ethernet frame.}
\label{erspanhdr}
\vspace{-1.0em}
\end{figure}

@@

In this section we describe the basic ERSPAN protocol header format
along with its implementation to Linux kernel.
For IPv4/IPv6, the implementation is under net/ipv4/ip\_gre.c and
net/ipv6/ip6\_gre.c. Also a userspace API header, include/uapi/linux/erspan.h
is added for metadata-mode tunnel users.

\subsection{Native v.s Metadata-Mode Tunnel}
%https://netdevconf.org/1.2/papers/borkmann.pdf
There are two tunnel type implementations in Linux kernel:
native tunnel and metadata-mode tunnel~\cite{lwtunnel}.
Native tunnel is the basic way of creating tunnels in Linux.
A tunnel netdev is created with per tunnel-specific configuration,
tied together with the netdev. For example, creating a GRE tunnel
with key and sequence number can be done by:
\texttt{ip link add dev gre123 type gretap local 1.1.1.1 remote 2.2.2.2 seq key 0xfb}.
As a result, $N$ different tunnel configurations require creating
$N$ number of netdevs.  In certain cases such as network virtualization,
this is not scalable because every host in the network creates
mutiple tunnels with different configurations to every other hosts~\cite{nvp}.

>>>>

\begin{figure}
{\scriptsize
\begin{verbatim}
                             Linux                    Linux
+----------+         +-------------------+      +---------------+
| Physical |         |     VM1  VM2 ...  |      |     linux     |
| Machines |         |      |    |       |      |    netdevs    |
+----------+         |  +--------------+ |      |      |        |
    | links          |  | Open vSwitch | |      | ERSPAN        |
    |                |  +--------------+ |      | netdev        |
+------------+       +-------||----------+      +-||------------+ 
|Cisco switch|               ||                   ||
+------------+               || ERSPAN            || ERSPAN
   || ERSPAN tunnel          || tunnel            || tunnel
   ||                        ||                   ||
    /~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\     +-------+ 
    {       Layer 3 IPv4, Ipv6 network             } === |Traffic|
    \~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~/     |Sniffer|
                                                         +-------+
\end{verbatim}   
}
\vspace{-0.5em}
\caption{Overview of the ERSPAN tunnel use cases. ERSPAN tunnels can be
created from a sniffer machine to Cisco switches, a Linux machine with
multiple VMs, or simply a Linux machine.}
\label{overview}
\vspace{-1.0em}
\end{figure}

ERSPAN is popular in the followin use cases~\cite{erspan_ietf}:
\begin{itemize}
\item Debugging network issues by tracking the control and data frames. 
\item Monitoring Voice-over-IP, VoIP, packets for delay and jitter analysis
\item Monitoring network transactions for latency analysis
\item Monitoring network traffic for anomaly detection
\end{itemize}
Figure~\ref{overview} shows an example setup of ERSPAN tunnels.
A network administrator first sets up multiple source network devices
and filters the interested portion of the traffic he/she wants
to inspect.  One case on the left-most is to create the ERSPAN tunnel
between the Cisco switch and a traffic sniffer.  Depending on the
features in the Cisco switch, different filters can be applied to the
traffic.  In the middle of the figure, for multiple virtual machines running
inside a Linux box, the virtual switch forwarding the packet between
virtual and physical network can also create ERSPAN tunnels between
the software switch and remote traffic sniffer.
Here, Open vSwitch~\cite{ovs} is an example capable of creating filters
and forward packets to ERSPAN tunnels. More detailed configurations of
Open vSwitch are described in later section.

@@

Mirrored traffic arrives at the sniffer machine needs to be able to
extract and restore the original monitored frame.  To differentiate
the three use cases, the administrator can create three ERSPAN session
ID, a configuration parameter for grouping the mirrored traffic.
For Linux user, an ERSPAN tunnel can also be used at the sniffer size.
Any packet arriving at the ERSPAN tunnel netdev's receive queue will
be decapsulated. Tools such as Wireshark~\cite{wireshark_erspan,wireshark_erspan2}
can be used to inspect the mirrored packet.

\section{ERSPAN Protocol Implementation}
\begin{figure}
{\scriptsize
\begin{verbatim}
<------------ outer -------------> <---- inner ---- ...
+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
| Ether |  IP  |  GRE  |  ERSPAN  | Ether |  IP  | ...   
+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
\end{verbatim}
}
\vspace{-1.0em}
\caption{An example of mirrored packet with outer header containing
the GRE and ERSPAN header, followed by the inner Ethernet frame.}
\label{erspanhdr}
\vspace{-1.0em}
\end{figure}

@@

In this section we describe the basic ERSPAN protocol header format
along with its implementation in the Linux kernel.
For IPv4/IPv6, the implementation is under net/ipv4/ip\_gre.c and
net/ipv6/ip6\_gre.c. Also a userspace API header, include/uapi/linux/erspan.h
is added for metadata-mode tunnel users.

\subsection{Native vs Metadata-Mode Tunnel}
%https://netdevconf.org/1.2/papers/borkmann.pdf
There are two tunnel type implementations in Linux kernel:
native tunnel and metadata-mode tunnel~\cite{lwtunnel}.
Native tunnel is the basic way of creating tunnels in Linux.
A tunnel netdev is created with per tunnel-specific configuration,
tied together with the netdev. For example, creating a GRE tunnel
with key and sequence number can be done by:
\texttt{ip link add dev gre123 type gretap local 1.1.1.1 remote 2.2.2.2 seq key 0xfb}.
As a result, $N$ different tunnel configurations require creating
$N$ number of netdevs.  In certain cases such as network virtualization,
this is not scalable because every host in the network creates
mutiple tunnels with different configurations to every other hosts~\cite{nvp}.
